Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-15 journal paper/content/sec-theory-proofs.tex
Inserted pointers re monotonicity-in-info lemma.

%\begin{proof}[Proof of Theorem~\ref{thm:random-greedy}]
  Let $\rewgr(n)$ denote the Bayesian-expected reward of the ``greedy
  choice'' after after $n-1$ steps of \alg[1]. Note that
  $\rew_1(\cdot)$ and $\rewgr(\cdot)$ are non-decreasing: the former
  because \alg[1] is monotone and the latter because the ``greedy
  choice'' is only improved with an increasing set of
  observations. \ascomment{insert a pointer} 
Using \eqref{eq:BIR-modification}, we conclude that
the greedy modification \alg[2] is monotone.

>>>>

%\begin{proof}[Proof of Theorem~\ref{thm:random-greedy}]
  Let $\rewgr(n)$ denote the Bayesian-expected reward of the ``greedy
  choice'' after after $n-1$ steps of \alg[1]. Note that
  $\rew_1(\cdot)$ and $\rewgr(\cdot)$ are non-decreasing: the former
  because \alg[1] is monotone and the latter because the ``greedy
  choice'' is only improved with an increasing set of
  observations, see Lemma~\ref{lm:MII}. 
Using \eqref{eq:BIR-modification}, we conclude that
the greedy modification \alg[2] is monotone.

### 2020-07-15 journal paper/content/sec-theory.tex
Added a note re monotone algs in theory/prelims.
Inserted pointers re monotonicity-in-info lemma.

@@

Second, let us argue that \alg[2] is monotone. This follows from \eqref{eq:BIR-modification} since both \alg[1] and \alggr are monotone. The latter follows from a ``monotonicity-in-information" property of the ``greedy step": essentially, it can only get better with more information
(see \ascomment{add a pointer}).

>>>>

An algorithm is called \emph{monotone} if it can only get better over time: $\rew_i(\cdot)$ is non-decreasing (and therefore $\BIR(\cdot)$ is non-decreasing). We argue this is a mild assumption, see
Appendix~\ref{app:MAB-monotone}.

@@

Second, let us argue that \alg[2] is monotone. This follows from \eqref{eq:BIR-modification} since both \alg[1] and \alggr are monotone. The latter follows from a ``monotonicity-in-information" property of the ``greedy step": essentially, it can only get better with more information
(see Lemma~\ref{lm:MII}).
